A generalized definition of multidimensional item response theory parameters

### 2023-02-17 output/paper_draft/paper_M2PLM_parameters.Rmd
Reorders and rewrites (WIP) the "test space" section

@@

AGREGADO
Aca pongo redacciön alternativa dejo igual la origunal debajo

We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of the discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces
Let us consider the model given by the equation (1 poner la referencia) where the latent traits and  the parameters $a_i$ are expressed in the same base B in their respective spaces.

Esta es la original

>>>>

********************************************************************************

We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of the
discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces.
Let us consider the model given by Equation \@ref(eq:M2PL-formulation),
where the latent traits and the parameters $`r DISCR_VECTOR`$ are expressed
in the same basis $`r LS_BASIS`$, in their respective spaces.
<!-- # TODO: Discuss; don't think this is actually true -->

********************************************************************************

@@
